Chapter 4

### 2021-08-04 thesis_chapter_4.Rmd
inital plot code

oude_spring <- tidync("OceanParcels/chapter_4_output/oudekraal_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_spring$season <- "Spring" 
oude_spring$site <- "Oudekraal" 
oude_spring <- oude_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_spring_mean$season <- "Spring" 
oude_spring_mean$site <- "Oudekraal"

@@

millers_spring <- tidync("OceanParcels/chapter_4_output/") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
millers_spring$season <- "Spring" 
millers_spring$site <- "Miller's Point" 
millers_spring_mean <- millers_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
millers_spring_mean$season <- "Spring" 
millers_spring_mean$site <- "Miller's Point"

@@

@@

>>>>

oude_spring <- tidync("OceanParcels/chapter_4_output/oudekraal_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
oude_spring$season <- "Spring" 
oude_spring$site <- "Oudekraal" 
oude_spring_mean <- oude_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
oude_spring_mean$season <- "Spring" 
oude_spring_mean$site <- "Oudekraal"

@@

millers_spring <- tidync("OceanParcels/chapter_4_output/millers_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
millers_spring$season <- "Spring" 
millers_spring$site <- "Miller's Point" 
millers_spring_mean <- millers_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
millers_spring_mean$season <- "Spring" 
millers_spring_mean$site <- "Miller's Point"

@@

buffels_summer <- tidync("OceanParcels/chapter_4_output/buffels_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
buffels_summer$season <- "Summer" 
buffels_summer$site <- "Buffelsbaai" 
buffels_summer_mean <- buffels_summer %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
buffels_summer_mean$season <- "Summer" 
buffels_summer_mean$site <- "Buffelsbaai"

buffels_autumn <- tidync("OceanParcels/chapter_4_output/buffels_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
buffels_autumn$season <- "Autumn" 
buffels_autumn$site <- "Buffelsbaai" 
buffels_autumn_mean <- buffels_autumn %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
buffels_autumn_mean$season <- "Autumn" 
buffels_autumn_mean$site <- "Buffelsbaai"

buffels_winter <- tidync("OceanParcels/chapter_4_output/buffels_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
buffels_winter$season <- "Winter" 
buffels_winter$site <- "Buffelsbaai" 
buffels_winter_mean <- buffels_winter %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
buffels_winter_mean$season <- "Winter" 
buffels_winter_mean$site <- "Buffelsbaai"

buffels_spring <- tidync("OceanParcels/chapter_4_output/buffels_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
buffels_spring$season <- "Spring" 
buffels_spring$site <- "Buffelsbaai" 
buffels_spring_mean <- buffels_spring %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:bathy, mean, na.rm= TRUE))
buffels_spring_mean$season <- "Spring" 
buffels_spring_mean$site <- "Buffelsbaai"

soetwater_summer <- tidync("OceanParcels/chapter_4_output/soetwater_summer.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
soetwater_summer$season <- "Summer"
soetwater_summer$site <- "Soetwater"
soetwater_summer_mean <- soetwater_summer %>% # calculate mean trajectory
  group_by(t) %>%
  summarise(across(lon:bathy, mean, na.rm= TRUE))
soetwater_summer_mean$season <- "Summer"
soetwater_summer_mean$site <- "Soetwater"

soetwater_autumn <- tidync("OceanParcels/chapter_4_output/soetwater_autumn.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
soetwater_autumn$season <- "Autumn"
soetwater_autumn$site <- "Soetwater"
soetwater_autumn_mean <- soetwater_autumn %>% # calculate mean trajectory
  group_by(t) %>%
  summarise(across(lon:bathy, mean, na.rm= TRUE))
soetwater_autumn_mean$season <- "Autumn"
soetwater_autumn_mean$site <- "Soetwater"

soetwater_winter <- tidync("OceanParcels/chapter_4_output/soetwater_winter.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
soetwater_winter$season <- "Winter"
soetwater_winter$site <- "Soetwater"
soetwater_winter_mean <- soetwater_winter %>% # calculate mean trajectory
  group_by(t) %>%
  summarise(across(lon:bathy, mean, na.rm= TRUE))
soetwater_winter_mean$season <- "Winter"
soetwater_winter_mean$site <- "Soetwater"

soetwater_spring <- tidync("OceanParcels/chapter_4_output/soetwater_spring.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, trajectory, lon, lat, distance, Salinity, age, KelpDepth, SinkSpeed,       KelpVelU, KelpVelV, VelU, VelV, WindU, WindV, bathy) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
soetwater_spring$season <- "Spring"
soetwater_spring$site <- "Soetwater"
soetwater_spring_mean <- soetwater_spring %>% # calculate mean trajectory
  group_by(t) %>%
  summarise(across(lon:bathy, mean, na.rm= TRUE))
soetwater_spring_mean$season <- "Spring"
soetwater_spring_mean$site <- "Soetwater"

@@

```{r message=FALSE, warning=FALSE}
# Summer
total_summer <- rbind(kom_summer_mean, houtbay_summer_mean, scar_summer_mean, oude_summer_mean, betty_summer_mean, kalk_summer_mean, aframe_summer_mean, sthelena_summer_mean, millers_summer_mean, baboon_summer_mean, basata_summer_mean, buffels_summer_mean, soetwater_summer_mean)

summer_mean <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 0.4, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2) +
  geom_path(data = total_summer, aes(x = lon, y = lat, linetype = site))+
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

# Autumn
total_autumn <- rbind(kom_autumn_mean, houtbay_autumn_mean, scar_autumn_mean, oude_autumn_mean, betty_autumn_mean, kalk_autumn_mean, aframe_autumn_mean, sthelena_autumn_mean, millers_autumn_mean, baboon_autumn_mean, basata_autumn_mean, buffels_autumn_mean, soetwater_autumn_mean)

autumn_mean <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 0.4, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2) +
  geom_path(data = total_autumn, aes(x = lon, y = lat, linetype = site))+
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

# Winter
total_winter <- rbind(kom_winter_mean, houtbay_winter_mean, scar_winter_mean, oude_winter_mean, betty_winter_mean, kalk_winter_mean, aframe_winter_mean, sthelena_winter_mean, millers_winter_mean, baboon_winter_mean, basata_winter_mean, buffels_winter_mean, soetwater_winter_mean)

winter_mean <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 0.4, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2) +
  geom_path(data = total_winter, aes(x = lon, y = lat, linetype = site))+
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
# Spring
total_spring <- rbind(kom_spring_mean, houtbay_spring_mean, scar_spring_mean, oude_spring_mean, betty_spring_mean, kalk_spring_mean, aframe_spring_mean, sthelena_spring_mean, millers_spring_mean, baboon_spring_mean, basata_spring_mean, buffels_spring_mean, soetwater_spring_mean)

spring_mean <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 0.4, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2) +
  geom_path(data = total_spring, aes(x = lon, y = lat, linetype = site))+
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12)) 
```

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggarrange(summer_mean, autumn_mean, winter_mean, common.legend = TRUE, font.label = list(size = 12, face = "bold"), legend = c("bottom"))

## Heatmaps

```{r message=FALSE, warning=FALSE}

## Load software need for entire script

load("map/south_africa_coast_hi_res.Rdata")
load("map/sa_bathy.RData")

aframe_summer_heatmap <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey", size = 0.2)+
  geom_hex(data = aframe_summer, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 68000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "gray") +
  geom_path(data = aframe_summer_mean,aes(x = lon, y = lat, color = 'red'), show.legend =     FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))
